
\documentclass{resume}

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Ahad Sheriff}
\address{(425)-677-5891 \\ ahadsheriff@gmail.com \\ ahadsheriff.com \\ github.com/ahadsheriff}

\begin{document}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Experience}

\begin{rSubsection}{Zoom}{\bf Seattle, WA}{\em \it Infrastructure Engineer}{\em \bf March 2021-Present}
\item 
Leading project to design, build, and maintain cloud infrastructure for a new Zoom service that is able to scale to millions of users. Provisioning cloud resources and deploying code across multiple cloud accounts, regions, and environments. Working closely with Engineering, Product, DevOps, and Security teams to determine requirements and deliver the project on time. Establishing processes to ensure the product is highly available and scalable. Conducting interviews with candidates to grow the team.
{\bf Tech Used: Kubernetes, Terraform, Helm, Prometheus, Grafana, Istio, Python, AWS, Gitlab}

{}{\bf}{\em \it DevOps Engineer}{\em \bf}
\item Managed deployments for Zoom's live streaming, conference room connectors, and audio conference services to deliver stable releases for thousands of international customers. Built end-to-end testing and monitoring tools to enable zero-downtime services. Helped engineers identify and fix software issues 3x faster by proposing a new monitoring strategy and automating thousands of alarms.
{\bf Tech Used: Kubernetes, Jenkins, Golang, Prometheus, AWS}
\end{rSubsection}

\begin{rSubsection}{VMware}{\bf Bellevue, WA}{\em \it Software Engineer}{\em \bf May 2019-April 2021}
\item 
Refined cloud resource policies across team to improve security and become SOC-2 compliant. Automated Kubernetes and AWS infrastructure using Ansible and Terraform for over 30 microservices, enabling reproducible development environments. Maintained code for Python command-line tool used by operators to interact with the product. Led effort to eliminate unused resources and reduce cloud spend. Participated in 24/7 on-call rotation. {\bf Tech Used: Kubernetes, Terraform, Ansible, Python, Golang, AWS}

{}{\bf}{\em \it Software Engineering Intern}{\em \bf}
\item Enhanced Jenkins CI/CD pipeline and Kubernetes infrastructure to get zero downtime deployments and improve product resiliency. Implemented Prometheus in Golang services to monitor application performance and visualize in Wavefront dashboards. Implemented a secret management solution to improve product security.
{\bf Tech Used: Kubernetes, Jenkins, Golang, Prometheus, AWS}
\end{rSubsection}

\begin{rSubsection}{Booz Allen Hamilton}{\bf McLean, VA}{\em \it Cyber Threat Intelligence Intern}{\em \bf June 2018-August 2018}
\item Analyzed threats, vectors, and actors in support of cyber defense operations. Worked closely with multiple security teams during incidents and drove response efforts. Conducted technical reviews of security events. Built a legacy database migration tool.
{\bf Tech Used: Splunk, Python, SQL}
\end{rSubsection}

\begin{rSubsection}{Citigroup}{\bf New York, NY}{\em \it Production Engineering Intern}{\em \bf January 2018-April 2018}
\item Built tools and devised automation strategies to improve uptime and health monitoring for trading infrastructure. Monitored high-frequency trading logs for bottlenecks and anomalies. Investigated events generated by the alerting pipeline and triage incidents.
{\bf Tech Used: Linux, Bash, FIX, Python}
\end{rSubsection}

% \begin{rSubsection}{Allied Associates International}{\bf Gainesville, VA}{\em \it Cyber Security Intern}{\em \bf June 2017-August 2017}
% \item Engineered a custom endpoint monitoring solution to detect malicious activity and meet Department of Defense requirements. Improved security posture by creating an incident response toolkit and auditing IT policy.
% {\bf Tech Used: Docker, Python, Elasticsearch, Logstash, Kibana, Suricata}
% \end{rSubsection}

\end{rSection}

%----------------------------------------------------------------------------------------
%	EDUCATION 
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf Rochester Institute of Technology, Rochester, NY} \hfill { \bf August 2015 - December 2019 }  
\\ \it Bachelor of Science, Computing Security\hfill {\bf }
%Minor in Psychology \smallskip \\

\end{rSection}

%--------------------------------------------------------------------------------
%    Projects
%-----------------------------------------------------------------------------------------------
\begin{rSection}{Projects}

\begin{rSubsection}{Crashdeck.io}{}{}{}
\item Developed a web based SaaS application to monitor JavaScript errors and alert developers in real-time. Designed system architecture and data processing pipeline to accommodate thousands of concurrent requests. Created product road-map and defined engineering requirements to launch beta in under 3 months.
{\bf Tech Used: Node, React, Python, Go, Postgres}
\end{rSubsection}

\end{rSection}


%	Achievements SECTION
%----------------------------------------------------------------------------------------

% \begin{rSection}{Achievements} 

% % \begin{rSubsection}{12for12}{}{\em \it President and Founder}{}
% % \item A 501c3 non-profit creating tools to make donating online easier. Received Microsoft Hack for Good grant. {\bf Tech Used: Vue.js, Node.js, Python, AWS Lambda, HTML, CSS}
% % \end{rSubsection}
% \begin{rSubsection}{Columbia University HealthHacks 2018}{}{\em \it First Place Winner}{}
% \item Built a mobile app to treat narcotic overdoses by facilitating communication between nearby reporters and those trained to treat overdoses. {\bf Tech Used: Swift, Firebase}
% \end{rSubsection}

% \end{rSection}

\end{document}
